### 2018-04-30 paper/security-discussion.tex
Writes up security discussion

\subsection{Limitations}%
\label{security-limitations}
from mails:

- Route fingerprinting in anonymous communications.

It depends on the random peer sampling I suppose. And I have no clue 
about how that one works. Adrien referred to a paper by Anne-Marie.

If I were to guess, I'd say: if Anne-Marie's RPS protocol is Byzantine 
fault tolerant, maybe; otherwise, we're most likely screwed.

> - Bridging and fingerprinting: Epistemic attacks on route selection

I'd say the same as above. It's about peer selection.

> - Breaking the collusion detection mechanism of morphmix

We don't do any collusion detection, so I'd say we're vulnerable. We 
assume we choose nodes uniformly at random, so colluding nodes have 
uniform probability of success --- but that falls back on the RPS and 
Anne-Marie's paper. So maybe or screwed.

> - Denial of service or denial of security? How attacks on reliability can
> compromise anonymity

After just reading the abstract, most likely vulnerable. But thanks to 
our stateless design we don't have to do retransmission the whole way, 
as might be the case for active circuits --- only the node who 
experience the failure going forward will need to retransmit. (Thanks Adrien for 
insisting on creating a route back for the ACK ;-) So we might not be in as bad 
a position as other systems, it'll take more rounds of attack to break it --- 
but I'm quite sure it will break.

But in general, these all face global and possibly malicious 
adversaries. We don't have that in our adversary model. If everyone 
colludes against Alice and Bob in our setting, they're screwed.

It's basically impossible to remain anonymous against the global 
adversary (statistical inference, paper by Danezis) unless Alice sends a 
message to everyone whenever she wants to send a message to Bob. 
Basically the anonymous communication community is converging on methods 
like Loopix and HORNET --- have enough throughput so that the global 
adversary is overwhelmed with data. (Tor is too slow.)

@@

We see two alternative paths for improving the header.
First, we might be able to adapt the Sphinx~\cite{Sphinx} cryptographic packet 
format to the routing of \(\SPOR\).
Then we could achieve the properties of Sphinx and enjoy provable security.

The second approach would be to use the technique by \textcite{PPACinPubFS}.
They adapt \(\ANOBE\) in such a way that its ciphertexts decrypt to different 
things for different recipients.
This way we could have one ciphertext encrypted for all the alternative nodes 
--- across layers.
Then the ciphertext would decrypt to different plaintexts for nodes on different 
layers in the route.
This would hide the path length (constant-size ciphertexts by padding) and the 
position of individual nodes.
This approach would probably be the easiest, but would probably not provide all 
the properties from Sphinx (\eg resistance to active tagging attacks and bitwise 
unlinkability).

>>>>

\subsection{Limitations}%
\label{security-limitations}

Many attacks against anonymous communications systems target the peer sampling 
mechanism, \eg~\cite{%
  RouteFingerprinting,%
  EpistemicAttacksOnRouteSelection,%
}.
So, even if our system is secure in theory, it will not be secure in practice 
unless the random peer sampling algorithm returns peers chosen uniformly 
randomly from the entire Global Device Retinue.

To prevent attacks on the random peer sampling, some systems have employed 
techniques to detect colluding nodes, \eg~\cite{%
  SecurePeerSampling,%
  MorphMix,%
}.
However, as is the case of~\cite{MorphMix}, these can be 
broken~\cite{BreakingMorphMix}.

There are also other types of attacks, \eg denial of service attacks that can 
lead to the adversary learning more from the system~\cite{DenialOfSecurity}.
It is difficult to say to what extent our system might be vulnerable to this 
type of attack without a deeper analysis.
Unfortunately this is outside the scope of this study.
However, we hypothesize that our stateless and redundant design might have some 
advantages, \eg no control messages sent back from where the error happened to 
the source.
But these advantages will only postpone the success of the attack, eventually 
even our protocol must resend.

@@

One thing that we can directly improve is the header.
We see two alternative paths for improving the header.
First, we might be able to adapt the Sphinx~\cite{Sphinx} cryptographic packet 
format to the routing of \(\SPOR\).
Then we could achieve the properties of Sphinx, \eg preventing the last node to 
learn the destination, and enjoy provable security.

The second approach would be to use the technique by \textcite{PPACinPubFS}.
They adapt \(\ANOBE\) in such a way that its ciphertexts decrypt to different 
things for different recipients.
This way we could have one ciphertext encrypted for all the alternative nodes 
--- across layers.
Then the ciphertext would decrypt to different plaintexts for nodes on different 
layers in the route.
This would hide the path length (constant-size ciphertexts by padding) and the 
position of individual nodes.
This approach would probably be the easiest, but would probably not provide all 
the properties from Sphinx (\eg resistance to active tagging attacks).
